BurgerMax Presents: Open Adcess

### 2017-03-31 introduction.tex
Mo citations mo problems
A couple of small changes

\section{Introduction}
Open access is a movement to make papers and other research contributions free
accessible to the general public \cite{oa}.
The ACM has been working for some time to achieve the open access dream but
have found this dream to be prohibitively expensive.
As such, we have required authors to opt-in to open access by paying the cost
themselves \todo{cite (and archive current authors.acm.org page)}.
However, we have found a way to provide open access papers at no cost to the
authors by adopting the techniques employed by various other websites and
publications that manage to distribute content for free.

Section~\ref{sec:related} details techniques used by other services to achieve free
downloads and paper distribution.
Section~\ref{sec:lib} describes the upcoming changes to the Digital Library to
bring it up to current standards for download portals.
Section~\ref{sec:sponsors} adapts techniques from tabloids to ensure that papers
themselves are profitable.
Section~\ref{sec:future} describes a future that directly results from the
publication of this paper.
We provide this look into the future so that we may attempt to contain the
beast that is the ACM while still providing free papers to all.

>>>>

\section{Introduction}
Open access is a movement to make papers and other research contributions
freely accessible to the general public \cite{oa}.
The ACM has been working for some time to achieve the open access dream but
have found this dream to be prohibitively expensive.
As such, we have required authors to opt-in to open access by paying the cost
themselves \cite{auth}.
However, we have found a way to provide open access papers at no cost to the
authors by adopting the techniques employed by various websites and
publications that manage to distribute content for free.

Section~\ref{sec:related} details techniques used by other services to achieve
free downloads and paper distribution.
Section~\ref{sec:lib} describes the upcoming changes to the Digital Library to
bring it up to the current standards for download portals.
Section~\ref{sec:sponsors} adapts techniques from tabloids to ensure that
the papers themselves are profitable.
Section~\ref{sec:future} provides work from a future that directly results from the present work.

### 2017-03-31 related-work.tex
Draft pass
A couple of small changes

Rapidshare \cite{rapidshare} was a website that provided rate limited free
downloads while simultaneously selling a paid download service that was
superior to the free tier.
This technique was meant to entice users to pay for the service.
Unfortunately, as Rapidshare no longer exists it seems that this technique
alone is insufficient to cover the costs of running a download service.
However, we still employ the technique as explained in \autoref{sec:limit} as a
supplemental revenue stream.

\todo{Harvest paper} and many other free rags employ heavy use of in paper ads,
native ads, and classifieds.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.

>>>>

Rapidshare \cite{rapidshare} was a website that provided rate-limited free
downloads while simultaneously selling a paid download service that was
superior to the free tier.
This technique was meant to entice users to pay for the service.
Unfortunately, as Rapidshare no longer exists, it seems that this technique, used alone, is insufficient to cover the costs of running a download service. Or maybe they did not take this technique far enough. He he he.

Free weeklies such as \emph{Wisdom} \cite{wisdom} employ such heavy use of print ads,
native ads, and classifieds that they may be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.
